Current State of Knowledge Representation Systems for Robotics

### 2011-12-01 krs-survey.tex
Typos

Several authors from fields that are connex to the robotics have previously listed desirable features of systems aiming at cognitive abilities as rich as possible.

@@

	\item nonmonotonic reasoning \fxfatal{give here a clear example},

@@

\cite{Hawes2008}: benchmarking of "Information-Processing Architectures on Intelligent Systems"
\subsubsection{Pyschological tests}
\label{sect|evaluation-tests}

@@

The main role of a knowledge represenation system is to provide an adequate
representation system to store facts and concepts that can be informally
described in natural language.

@@

Most (but not all) of the systems we survey rely on a particular logic
formalism. The choice of the formalism has a strong impact, on one side, on the
range of ideas that can be expressed conveniently (\emph{practical
expressiveness}) or at all (\emph{theoritical expressiveness}), on the other
side, on the ability to solve the inference problem (called
\emph{decidability}: is a given logical sentence true in my model?) in a
tractable manner.

@@

One last class of logics that is of particular relevance for robotic
applications is the \emph{probabilistic logics} or \emph{bayesian logics}.
These logics provide a formal framework to reason on propositions whose truth
or falsity is uncertain. We elaborate below on the representation of uncertainty.

@@

This distinction is important in robotics were the robot may have to manipulate
concepts with only partial knowledge on them. For instance, let imagine a robot
that sees a bottle over a table, whose bottom is hidden by another object. The
robot can not prove that the bottle is indeed \emph{on} the table. A knowledge
representation system relying on the closed world assumption would then assume
the bottle is \emph{not} on the table ($\lnot R^{CWA}_{isOn}(bottle, table)$)
whereas with the open world assumption, the proposition $R^{OWA}_{isOn}(bottle,
table)$ would be undecided. Example in table~\ref{table|cwa-owa-example} provides
a simple, concerete example of consequences of the CWA/OWA choice on reasoning.

\begin{table}
	\begin{center}
	\begin{tabular}{ll}
	{\bf Action} & {\bf Part involved} \\
	\hline
	{\tt PickSoftly} & hand \\
	{\tt PickAndPlace} & arm, hand \\
	{\tt MoveArm} & arm \\
	\hline
	\end{tabular}
	\end{center}
	\caption{Assuming the question is: \emph{select actions that do not require
	to move the arm}, a CWA reasoner would return {\tt PickSoftly} whereas an
	OWA reasoner would not return anything if the {\tt PickSoftly} action is
	not explicitely said not to involve the arm.}
	\label{table|cwa-owa-example}
\end{table}

@@

Sources of uncertainty for a robot are two-fold: uncertainty \emph{intrinsic}
to facts (like \emph{``It may rain tomorrow''}), uncertainty caused by
imperfect perception of the world (\emph{``Is the bottle really on the
table?''}). Most logics do not account explicitely for uncertainty. It must be
either relied on specific logics (like Bayesian logics) or on extensions of
classical logics.

@@

\begin{quotation}
Consider putting an axiom in a common sense database asserting that birds can
fly. Clearly the axiom must be qualified in some way since penguins, dead birds
and birds whose feet are encased in concrete can't fly. A careful construction
of the axiom might succeed in including the exceptions of penguins and dead
birds, but clearly we can think up as many additional exceptions like birds
with their feet encased in concrete as we like. Formalized nonmonotonic
reasoning provides a way of saying that a bird can fly unless there
is an abnormal circumstance and reasoning that only the abnormal circumstances
whose existence follows from the facts being taken into account will be
considered.
\end{quotation}

@@

A monotonic system does not theoritically allow for knowledge retractation,
which is an important issue in the robotic context where the world model is
likely to be often altered.  However it is a practical issue only if the
reasoning process is \emph{continuous} during the whole robot's activity
lifespan. It is often possible to stop the reasoner, alter the knowledge, and
restart the inference process on a new domain.
\fxfatal{Rephrase to emphazise that when new evidences appear, it is anyway often a
good idea to restart the reasoner.}

@@

\subsubsection{Presupposition accomodation}
\label{sect|presupposition-accomodation}

\emph{Presupposition accomodation} is the ability for the system to
automatically create a context allowing to make sense of a proposition.

>>>>

Several authors from fields that are connected to the robotics have previously listed desirable features of systems aiming at cognitive abilities as rich as possible.

@@

	\item non-monotonic reasoning \fxfatal{give here a clear example},

@@

\cite{Hawes2008}: benchmarking of "Information-Processing Architectures on Intelligent Systems"
\subsubsection{Psychological tests}
\label{sect|evaluation-tests}

@@

The main role of a knowledge representation system is to provide an adequate
representation system to store facts and concepts that can be informally
described in natural language.

@@

Most (but not all) of the systems we survey rely on a particular logic
formalism. The choice of the formalism has a strong impact, on one side, on the
range of ideas that can be expressed conveniently (\emph{practical
expressiveness}) or at all (\emph{theoretical expressiveness}), on the other
side, on the ability to solve the inference problem (called
\emph{decidability}: is a given logical sentence true in my model?) in a
tractable manner.

@@

One last class of logics that is of particular relevance for robotic
applications is the \emph{probabilistic logics} or \emph{Bayesian logics}.
These logics provide a formal framework to reason on propositions whose truth
or falsity is uncertain. We elaborate below on the representation of uncertainty.

@@

This distinction is important in robotics were the robot may have to manipulate
concepts with only partial knowledge on them. For instance, let imagine a robot
that sees a bottle over a table, whose bottom is hidden by another object. The
robot can not prove that the bottle is indeed \emph{on} the table. A knowledge
representation system relying on the closed world assumption would then assume
the bottle is \emph{not} on the table ($\lnot R^{CWA}_{isOn}(bottle, table)$)
whereas with the open world assumption, the proposition $R^{OWA}_{isOn}(bottle,
table)$ would be undecided. Example in table~\ref{table|cwa-owa-example} provides
a simple, concrete example of consequences of the CWA/OWA choice on reasoning.

\begin{table}
	\begin{center}
	\begin{tabular}{ll}
	{\bf Action} & {\bf Part involved} \\
	\hline
	{\tt PickSoftly} & hand \\
	{\tt PickAndPlace} & arm, hand \\
	{\tt MoveArm} & arm \\
	\hline
	\end{tabular}
	\end{center}
	\caption{Assuming the question is: \emph{select actions that do not require
	to move the arm}, a CWA reasoner would return {\tt PickSoftly} whereas an
	OWA reasoner would not return anything if the {\tt PickSoftly} action is
	not explicitly said not to involve the arm.}
	\label{table|cwa-owa-example}
\end{table}

@@

Sources of uncertainty for a robot are two-fold: uncertainty \emph{intrinsic}
to facts (like \emph{``It may rain tomorrow''}), uncertainty caused by
imperfect perception of the world (\emph{``Is the bottle really on the
table?''}). Most logics do not account explicitly for uncertainty. It must be
either relied on specific logics (like Bayesian logics) or on extensions of
classical logics.

@@

\begin{quotation}
Consider putting an axiom in a common sense database asserting that birds can
fly. Clearly the axiom must be qualified in some way since penguins, dead birds
and birds whose feet are encased in concrete can't fly. A careful construction
of the axiom might succeed in including the exceptions of penguins and dead
birds, but clearly we can think up as many additional exceptions like birds
with their feet encased in concrete as we like. Formalized non-monotonic
reasoning provides a way of saying that a bird can fly unless there
is an abnormal circumstance and reasoning that only the abnormal circumstances
whose existence follows from the facts being taken into account will be
considered.
\end{quotation}

@@

A monotonic system does not theoretically allow for knowledge retractation,
which is an important issue in the robotic context where the world model is
likely to be often altered.  However it is a practical issue only if the
reasoning process is \emph{continuous} during the whole robot's activity
lifespan. It is often possible to stop the reasoner, alter the knowledge, and
restart the inference process on a new domain.
\fxfatal{Rephrase to emphasize that when new evidences appear, it is anyway often a
good idea to restart the reasoner.}

@@

\subsubsection{Presupposition accommodation}
\label{sect|presupposition-accomodation}

\emph{Presupposition accommodation} is the ability for the system to
automatically create a context allowing to make sense of a proposition.
